---
title: "Up and running with `blogdown`"
author: "Alison Presmanes Hill"
date: '2017-05-16'
tags: blogdown
categories: R
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, eval = FALSE)
```

# Read up on blogdown

Before you start, I recommend reading the following:

* ["blogdown: Creating Websites with R Markdown" by Yihui Xie and Amber Thomas](https://bookdown.org/yihui/blogdown/)
* ["Making a Website Using Blogdown, Hugo, and GitHub pages" by Amber Thomas](https://proquestionasker.github.io/blog/Making_Site/)
* ["Getting Started with Blogdown" by M. Edward (Ed) Borasky](https://www.znmeb.mobi/2017/05/12/getting-started-with-blogdown/)

I also found a comment by Eric Nantz, the creator [the R-Podcast](http://r-podcast.org), in the [`rbind/support` issues section on Github] (https://github.com/rbind/support) to be helpful:

* [https://github.com/rbind/support/issues/12](https://github.com/rbind/support/issues/12)

# Start in R/RStudio console

* First, I installed `blogdown` in my RStudio console (your working directory doesn't matter here) by running these commands:

```{r}
if (!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("rstudio/blogdown")
```

* Still in my RStudio console, I used the `blogdown` package to run the `install_hugo` function (again, your working directory doesn't matter here): 

```{r}
blogdown::install_hugo()
# or
# library(blogdown)
# install_hugo()
```

# Go to Github

* Next, I went to Github online and set up a new repository. If you are going to use Netlify to host the site, rather than Github pages, you can name this repository anything!
    - If you want to host your site through Github, you should follow Amber's instructions and lead and name your repository `yourgithubname.github.io`
    
# To the terminal!
    
* Then I opened up terminal, and used `cd` to navigate into the directory I wanted, and then typed:
`git clone https://github.com/apreshill/apreshill.git`

This is what subsequently printed in my terminal window:

```{r eval = FALSE}
ORPA473:r-projects hillali$ git clone https://github.com/apreshill/apreshill.git
Cloning into 'apreshill'...
remote: Counting objects: 3, done.
remote: Compressing objects: 100% (2/2), done.
remote: Total 3 (delta 0), reused 0 (delta 0), pack-reused 0
Unpacking objects: 100% (3/3), done.
Checking connectivity... done.
ORPA473:r-projects hillali$ 
```

# Back to RStudio!

* Go to File --> New Project --> Existing directory, then I pointed RStudio to [insert image here]

* Now, edit your `*gitignore` file. I opened mine from RStudio but you can use any text editor to open and edit this file. Below is what it should look like: the first four lines will automatically be in this file if you have set up your RStudio Project, but you need to add the `public/` line.

```{r eval = FALSE}
.Rproj.user
.Rhistory
.RData
.Ruserdata
public/
```


* Fihnally you can start to build your site using the `blogdown::new_site()` function. But first you should know...

    - If you want a theme other than the default, which is the lithium theme, you can do this now!
    
```{r}
# for example, create a new site with the academic theme
blogdown::new_site(theme = "gcushen/hugo-academic")
```

    
    - If instead you want to add the theme (like I did, because I didn't see the above example until it was too late!), use this function:
    
```{r}
install_theme("gcushen/hugo-academic", theme_example = TRUE, update_config = TRUE)
```




# Including Plots

You can also embed plots. See Figure \@ref(fig:pie) for example:

```{r pie, fig.cap='A fancy pie chart.', tidy=FALSE}
par(mar = c(0, 1, 0, 1))
pie(
  c(280, 60, 20),
  c('Sky', 'Sunny side of pyramid', 'Shady side of pyramid'),
  col = c('#0292D8', '#F7EA39', '#C4B632'),
  init.angle = -50, border = NA
)
```
