---
title: Up and running with blogdown
author: Alison Presmanes Hill
date: '2017-05-17'
slug: up-and-running-with-blogdown
categories:
  - R
tags: [blogdown]
summary: A quick guide to getting up and running with blogdown, Github, and Netlify
---

```{r include = FALSE}
knitr::opts_chunk$set(eval = FALSE, collapse = TRUE, comment = NA, tidy = FALSE)
```


# Read up on blogdown

Before you start, I recommend reading the following:

* ["blogdown: Creating Websites with R Markdown" by Yihui Xie and Amber Thomas](https://bookdown.org/yihui/blogdown/)
* ["Making a Website Using Blogdown, Hugo, and GitHub pages" by Amber Thomas](https://proquestionasker.github.io/blog/Making_Site/)
* ["Getting Started with Blogdown" by M. Edward (Ed) Borasky](https://www.znmeb.mobi/2017/05/12/getting-started-with-blogdown/)

I also found a comment by Eric Nantz, the creator [the R-Podcast](http://r-podcast.org), in the [`rbind/support` issues section on Github](https://github.com/rbind/support) to be helpful:

* [https://github.com/rbind/support/issues/12](https://github.com/rbind/support/issues/12)

# Start in R/RStudio console

1. First, I installed `blogdown` in my RStudio console (your working directory doesn't matter here). If you already have `devtools` installed like I did, you can just use the second line below:

```{r}
if (!requireNamespace("devtools")) install.packages("devtools")
devtools::install_github("rstudio/blogdown")
```

1. Still in my RStudio console, I used the `blogdown` package to run the `install_hugo` function (again, your working directory doesn't matter here): 

```{r}
blogdown::install_hugo()
# or
# library(blogdown)
# install_hugo()
```

# Go to Github

1. Go online to [Github](https://github.com) and create a new repository. A few things you need to know now:

* If you are going to use Netlify to host the site, rather than Github Pages, you can name this repository anything!
* If you want to host your site as a Github Page, you should name your repository `yourgithubusername.github.io`
    
# Open up your terminal

Or your alternative command line tool for a Windows machine.
    
* Then open up terminal, and use `cd` to navigate into the directory where you want your repo to be, and then type:
`git clone https://github.com/apreshill/apreshill.git`

This is what subsequently printed in my terminal window:

```{r eval = FALSE}
ORPA473:r-projects hillali$ git clone https://github.com/apreshill/apreshill.git
Cloning into 'apreshill'...
remote: Counting objects: 3, done.
remote: Compressing objects: 100% (2/2), done.
remote: Total 3 (delta 0), reused 0 (delta 0), pack-reused 0
Unpacking objects: 100% (3/3), done.
Checking connectivity... done.
ORPA473:r-projects hillali$ 
```

# Back to RStudio!

* Go to File --> New Project --> Existing directory, then I pointed RStudio to [insert image here]

* Now, edit your `*gitignore` file. I opened mine from RStudio but you can use any text editor to open and edit this file. Below is what it should look like: the first four lines will automatically be in this file if you have set up your RStudio Project, but you need to add the `public/` line.

```{r eval = FALSE}
.Rproj.user
.Rhistory
.RData
.Ruserdata
public/
```


* Finally you can start to build your site using the `blogdown::new_site()` function. But first you should know...

    - If you want a theme other than the default, which is the lithium theme, you can do this now!
    
```{r}
# for example, create a new site with the academic theme
blogdown::new_site(theme = "gcushen/hugo-academic")
```

    
    - If instead you want to add the theme (like I did, because I didn't see the above example until it was too late!), use this function:
    
```{r}
install_theme("gcushen/hugo-academic", theme_example = TRUE, update_config = TRUE)
```




