---
title: Making a data package for teaching
author: ''
date: '2018-07-01'
slug: repro-health
categories: []
tags: []
draft: TRUE
---

```{r include = FALSE}
knitr::opts_chunk$set(eval = FALSE, collapse = TRUE, comment = NA, tidy = FALSE)
```

First created a github repo, cloned locally into an R project.

## Create the package

```{r}
# Create a new package -------------------------------------------------
library(usethis)
library(here)

create_package(here::here()) # could have also used getwd()
```

screenshot here

## Add dependencies

```{r}
deps <- c("dplyr", "tidyr", "readr", "stringr", "janitor", "purrr", "ggplot2", "wbstats", "gapminder")
library(purrr)
walk(deps, usethis::use_package, type = "Suggests")
```

# Add license

```{r}
use_mit_license("Alison Hill")
```

# Updated DESCRIPTION

basically copied from jenny's 
https://github.com/jennybc/gapminder/blob/master/DESCRIPTION

# Make and edit news + readme
```{r}
use_news_md()
use_readme_rmd()
```

# Make package docs
```{r}
use_package_doc()
```

creates new R script in `R` folder, just help page for whole package like `?globalwomen`

this updated the description file
```{r}
use_roxygen_md()
```

NOW TWO TO-DO ITEMS
-vignettes
-setting up documentation (everything in `R` folder is where `roxygen` will look for stuff to put automatically in `man` folder as .Rd files)