---
title: How to build a data package in R
author: ''
date: '2018-06-29'
slug: data-package
categories: []
tags: []
draft: TRUE
---

```{r global_options, include = FALSE}
knitr::opts_chunk$set(eval = FALSE, comment = "#")
```

-Made the package
-Dependencies
-Edit description
- add license
- add vignette
- add news
- add readme

## Create the package

```{r}
# Create a new package -------------------------------------------------
library(usethis)
library(here)

create_package(here::here()) # could have also used getwd()
```

What did this step do?

## Add dependencies

```{r}
use_package(c("rvest", "dplyr", "tidyr", "readr", "stringr", "janitor", "purrr", "lubridate", "ggplot2"), type = "Suggests")
```

```
Error in use_package(c("rvest", "dplyr", "tidyr", "readr", "stringr",  : 
  could not find function "use_package"
```

```{r}
deps <- c("rvest", "dplyr", "tidyr", "readr", "stringr", "janitor", "purrr", "lubridate", "ggplot2")
library(purrr)
walk(deps, usethis::use_package, type = "Suggests")
```

add license
after updating description with persons and SAVING
```{r}
use_mit_license("Alison Hill")
use_vignette("bakeoffs-abroad")
```

note: very important! In authors there is a blank in the vector `, ,`. If you delete this you'll get a crazy error later on:
```{r eval = FALSE}
roxygen2::roxygenise()
It is recommended to use ‘given’ instead of ‘middle’.
It is recommended to use ‘given’ instead of ‘middle’.
Error in vapply(unclass(authors), author_desc, character(1)) : 
  values must be length 1,
 but FUN(X[[1]]) result is length 2
```

I should have left the space in, or specified `email = ` for the third argument, becuase the function `person` assumed this was my middle name.

make news + readme
```{r}
use_news_md()
use_readme_rmd()
```

in read me
```{r}
# install.packages("remotes")
remotes::install_github("apreshill/bakeoff")
```

package docs
```{r}
use_package_doc()
```

creates new R script in `R` folder, just help page for whole package like `?bakeoff`

this updated the description file
```{r}
use_roxygen_md()
```

Roxygen: list(markdown = TRUE)
RoxygenNote: 6.0.1

TWO MAIN THINGS
-vignettes
-setting up documentation (everything in `R` folder is where `roxygen` will look for stuff to put automatically in `man` folder as .Rd files)

may need: https://github.com/rudeboybert/fivethirtyeight/blob/master/data_import_procedure.md

I edited bakeoff-package.R using https://github.com/rudeboybert/fivethirtyeight/blob/master/R/fivethirtyeight.R

Now `man` is empty though! Need to get stuff from `R` file into `man` using `roxygen`. Note that good stuff on roxygen in the R packages cheatsheet.

Two ways- see screen shots OR
```{r}
roxygen2::roxygenise()
```

> roxygen2::roxygenise()
It is recommended to use ‘given’ instead of ‘middle’.
It is recommended to use ‘given’ instead of ‘middle’.
Error in vapply(unclass(authors), author_desc, character(1)) : 
  values must be length 1,
 but FUN(X[[1]]) result is length 2
> ?roxygenise
> roxygen2::roxygenise()
Writing NAMESPACE
Writing bakeoff-package.Rd
Writing bakeoff.Rd

Now switching to `devtools`
we are going to build this thing
keyboard shortcut COMMAND SHIFT B
then see if we type `?bakeoff` that we get the help page.
see screenshot-successful build!

it loaded the package for me
```{r eval = FALSE}
library(bakeoff)
Warning message:
package ‘purrr’ was built under R version 3.4.4 
?bakeoff
```
see screenshot!!! success! chester: BAM!

make a package down site, didn't need to have `pkg_down` installed for this to work...
```{r eval = FALSE}
> use_pkgdown()
● Modify '_pkgdown.yml'
✔ Adding '^_pkgdown\\.yml$' to '.Rbuildignore'
✔ Creating 'docs/'
✔ Adding '^docs$' to '.Rbuildignore'
```

(can edit `_pkgdown.yml`): https://github.com/andrewpbray/infer/blob/develop/_pkgdown.yml

tehn you can build your damn site with pkgdown

but now you need the actual package
```{r}
library(pkgdown)
```

```{r}
pkgdown::build_site()
```

build_site every time, creates static site in `docs` folder.

now push to github

enable site see screenshot

look on 538:

https://github.com/rudeboybert/fivethirtyeight/tree/master/data-raw

make a script to create `data/` from `data-raw/` automatically:

use R script `process_data_sets.R` in `data-raw/`--> takes csv files as input, do some additional taming, outputs rda files (overwrite = TRUE) using `usethis::use_data()` to output `data/`


i wanted to update description like njtierney to have my orcid there

2 steps:
- build package (command shift b) (`devtools::build()`)

now: how to actually document a dataset
1) workflow: keep roxygenized script open for each dataset like bakers as `bakers.R` in `R` folder
2) also open a data-process.R in `data-raw/` and edit back and forth as tabs, so `bakers-process.R` this file MUST use `usethis::use_data`, can't just have .rda files in a `data/` folder for it to work.

ok future stuff: enable docsearch (https://daattali.gitbooks.io/stat545-ubc-github-io/bit003_api-key-env-var.html) like nick tierney
- `pkgdown::build_site()`
---
for dplyr edits: i edited the file in R folder, checked in man, so it was actually roxygenized. is it updated in docs/reference?

